---
title: "HW6_Sonam"
author: "sonam.rathod@rutgers.edu"
date: "2024-11-16"
output: html_document
---

#### Find an independent variable to predict your time-series (2 points)

**Dependent variable** - the number of baggage complaints (Baggage)

**Independent variables** - Scheduled, Cancelled, and Enplaned

```{r}
library(forecast)
library(ggplot2)

baggagecomplaints <- read.csv("~/Downloads/baggagecomplaints.csv")
plot(baggagecomplaints$Scheduled, baggagecomplaints$Baggage,
     xlab = "Scheduled Flights",
     ylab = "Baggage Complaints",
     main = "Baggage Complaints vs. Scheduled Flights")

plot(baggagecomplaints$Enplaned, baggagecomplaints$Baggage,
     xlab = "Enplaned Passengers",
     ylab = "Baggage Complaints",
     main = "Baggage Complaints vs. Enplaned Passengers")

# Plot Baggage vs. Cancelled
plot(baggagecomplaints$Cancelled, baggagecomplaints$Baggage,
     xlab = "Cancelled Flights",
     ylab = "Baggage Complaints",
     main = "Baggage Complaints vs. Cancelled Flights")

pairs(~ Baggage + Scheduled + Enplaned + Cancelled, data = baggagecomplaints,
      main = "Pairwise Scatter Plots")
numeric_data <- baggagecomplaints[, !(names(baggagecomplaints) %in% c("Month", "Year", "Airline"))]

numeric_data <- numeric_data[, sapply(numeric_data, is.numeric)]
cor(numeric_data)
```

##### Based on correlation matrix, Baggage complaints has highest correlation with Schedule (0.81744), hence, selecting Scheduled as the independent variable for predicting baggage complaints.


#### Perform regression (2 Points)
```{r}
mfit <- lm(Baggage ~ Scheduled, data = baggagecomplaints)
plot(baggagecomplaints$Scheduled, baggagecomplaints$Baggage, col = "blue", pch=19,
     main = "Baggage Complaints vs. Scheduled Flights",
     xlab = "Scheduled Flights", ylab = "Baggage Complaints")
abline(mfit, col = "red", lwd = 2)
```

#### Perform Model Acceptance Steps and show the interpretation of the model output (3 Points)
```{r}
summary(mfit) 
```

When there are zero scheduled flights, the predicted number of baggage complaints is -830.02, which is practically not possible.
For every additional scheduled flight, the number of baggage complaints is predicted to increase by 0.4779 on average. The coefficient is highly significant with p-value.
Multiple R-squared:  0.6682, Adjusted R-squared:  0.6669 66.8% of the variance in Baggage is explained by Scheduled.

F-statistic = 503.5, p-value < 2.2e-16:
The model is highly significant. This confirms that the Scheduled flight has a significant impact on the Baggage Complaints.

#### Perform Residual Analysis and explain the insights (3 Points)
```{r}
res <- residuals(mfit)
hist(res, main = "Histogram of Residuals", xlab = "Residuals")

```

The histogram shows that the residuals are asymmetric, there appears to be some skewness.

```{r}
plot(res ~ baggagecomplaints$Scheduled, 
     xlab = "Scheduled Flights", ylab = "Residuals",
     main = "Residuals vs Scheduled Flights", pch = 19, col = "blue")
abline(h = 0, col = "red", lty = 2)
```

The residuals are generally scattered around zero with no clear pattern. This indicates that the linear model is appropriately capturing the relationship between Scheduled Flights and Baggage Complaints.

```{r}
library(forecast)
forecast_val <- forecast(mfit, newdata = data.frame(Scheduled = 50000))
print(forecast_val)
plot(forecast_val, xlab = "Scheduled Flights", ylab = "Baggage Complaints")
confint(mfit, level = 0.95)

par(mfrow = c(1, 2)) # Split plot area
fit_log <- lm(log(baggagecomplaints$Baggage) ~ log(baggagecomplaints$Scheduled), data = baggagecomplaints)

# Plot 1: Original Scale
plot(Baggage ~ Scheduled, data = baggagecomplaints, 
     xlab = "Scheduled Flights", ylab = "Baggage Complaints",
     main = "Original Scale",
     pch = 19, col = "blue")
lines(1:max(baggagecomplaints$Scheduled), exp(fit_log$coef[1] + fit_log$coef[2] * log(1:max(baggagecomplaints$Scheduled))), col = "red")

# Plot 2: Log-Log Scale
plot(log(baggagecomplaints$Baggage) ~ log(baggagecomplaints$Scheduled), data = baggagecomplaints, 
     xlab = "Log(Scheduled Flights)", ylab = "Log(Baggage Complaints)",
     main = "Log-Log Scale",
     pch = 19, col = "blue")
abline(fit_log, col = "red")

# Residual Plot for Transformed Model
par(mfrow = c(1, 1)) # Reset plot area
log_res <- residuals(fit_log)
plot(log_res ~ log(baggagecomplaints$Scheduled), 
     xlab = "Log(Scheduled Flights)", ylab = "Residuals",
     main = "Residuals for Log-Transformed Model",
     pch = 19, col = "blue")
abline(h = 0, col = "red", lty = 2)
```

### Multiple regression

```{r}
multi_model <- lm(baggagecomplaints$Baggage ~ baggagecomplaints$Scheduled + baggagecomplaints$Cancelled + baggagecomplaints$Enplaned, data = baggagecomplaints)
summary(multi_model)

coefficients(multi_model)  
confint(multi_model, level = 0.95) 

# Residual Analysis
# Residuals vs Fitted
plot(multi_model$fitted.values, residuals(multi_model), 
     xlab = "Fitted Values", ylab = "Residuals",
     main = "Residuals vs Fitted Values", pch = 19, col = "blue")
abline(h = 0, col = "red", lty = 2)

# Histogram of Residuals
hist(residuals(multi_model), main = "Histogram of Residuals", 
     xlab = "Residuals", border = "black")

```

Each canceled flight increases complaints. Schedule flight has moderate impact whereas Enplaned has small impact on baggage complaints. 