---
title: "HW7_Sonam"
author: "Sonam Rathod"
date: "2024-11-21"
output: html_document
---

# ARIMA

#### 1. Explain the output
```{r}
library(dplyr)
library(forecast)
baggagecomplaints <- read.csv("~/Downloads/baggagecomplaints.csv")

baggageUnited <- baggagecomplaints %>%
  filter(Airline == "United")

united_ts <- ts(baggageUnited$Baggage, start = c(2004, 1), end = c(2010,12), frequency = 12)
plot(united_ts, main = "Monthly Complaints (United Airlines)", xlab = "Year", ylab = "Complaints")

baggageAmerican <- baggagecomplaints %>%
  filter(Airline == "American Eagle")

american_ts <- ts(baggageAmerican$Baggage, start = c(2004, 1), end = c(2010,12), frequency = 12)
plot(american_ts, main = "Monthly Complaints (American Eagle)", xlab = "Year", ylab = "Complaints")

baggageHawaiian <- baggagecomplaints %>%
  filter(Airline == "Hawaiian")

hawaiian_ts <- ts(baggageHawaiian$Baggage, start = c(2004, 1), end = c(2010,12), frequency = 12)
plot(hawaiian_ts, main = "Monthly Complaints (Hawaiian)", xlab = "Year", ylab = "Complaints")

# United Airlines ARIMA

united_model <- auto.arima(united_ts, trace = TRUE, stepwise = FALSE)
summary(united_model)

# American Eagle ARIMA
american_model <- auto.arima(american_ts, trace = TRUE, stepwise = FALSE)
summary(american_model)

# Hawaiian ARIMA
hawaiian_model <- auto.arima(hawaiian_ts, trace = TRUE, stepwise = FALSE)
summary(hawaiian_model)
```

**United Airlines** Best model: ARIMA(0,1,0)(2,1,0)[12]

1. No autoregressive terms are included.

2. Data was differenced once to achieve stationarity.

3. No moving average terms are included.

4. The model predicts with an average error of 11.61% relative to the observed values.

**American Eagle** Best model: ARIMA(3,1,1)(0,1,1)[12]

1. The data was differenced once to make it stable.

2. The model uses 1 moving average term

3. The model uses 3 autoregressive terms

4. Predictions are off by 8.77% on average, indicating high accuracy 

**Hawaiian** Best model: ARIMA(1,0,0) 

1. The model includes 1 autoregressive term.

2. The data was already stable, so no differencing was needed.

3. No moving average (MA) component is used.

4. MAPE (13.46%): Predictions are about 13.46% off from actual complaints on average.


#### 2. Run Residual Analysis
```{r}
united_residuals <- residuals(united_model)
american_residuals <- residuals(american_model)
hawaiian_residuals <- residuals(hawaiian_model)

residuals_df <- data.frame(
  Time = time(united_residuals),
  United = as.numeric(united_residuals),
  American = as.numeric(american_residuals),
  Hawaiian = as.numeric(hawaiian_residuals)
)

par(mfrow = c(3, 1))
plot(united_residuals, main = "Residuals for United Airlines", ylab = "Residuals", col = "blue")
abline(h = 0, col = "red", lty = 2)
plot(american_residuals, main = "Residuals for American Eagle", ylab = "Residuals", col = "green")
abline(h = 0, col = "red", lty = 2)
plot(hawaiian_residuals, main = "Residuals for Hawaiian Airlines", ylab = "Residuals", col = "purple")
abline(h = 0, col = "red", lty = 2)

par(mfrow = c(3, 1))
hist(united_residuals, main = "Histogram of Residuals (United)", col = "blue", xlab = "Residuals")
hist(american_residuals, main = "Histogram of Residuals (American Eagle)", col = "green", xlab = "Residuals")
hist(hawaiian_residuals, main = "Histogram of Residuals (Hawaiian)", col = "purple", xlab = "Residuals")


par(mfrow = c(3, 1))
Acf(united_residuals, main = "ACF of Residuals (United)")
Acf(american_residuals, main = "ACF of Residuals (American Eagle)")
Acf(hawaiian_residuals, main = "ACF of Residuals (Hawaiian)")

united_lb <- Box.test(united_residuals, lag = 20, type = "Ljung-Box")
american_lb <- Box.test(american_residuals, lag = 20, type = "Ljung-Box")
hawaiian_lb <- Box.test(hawaiian_residuals, lag = 20, type = "Ljung-Box")

print("Ljung-Box Test Results:")
print(united_lb)
print(american_lb)
print(hawaiian_lb)

residual_stats <- data.frame(
  Airline = c("United", "American Eagle", "Hawaiian"),
  Variance = c(var(united_residuals), var(american_residuals), var(hawaiian_residuals)),
  Mean = c(mean(united_residuals), mean(american_residuals), mean(hawaiian_residuals)),
  SD = c(sd(united_residuals), sd(american_residuals), sd(hawaiian_residuals))
)
print(residual_stats)

```

**United Airlines** - The distribution is centered around zero, which suggests normal distribution.

**American Eagle** - The histogram shows a reasonably symmetrical distribution around zero.

**Hawaiian** - The histogram shows a symmetrical distribution around zero.

#### 3. Perform and Plot the forecast for the next five periods
```{r}
united_forecast <- forecast(united_model, h = 5)
plot(united_forecast, main = "5-Month Forecast for United Airlines", xlab = "Year", ylab = "Complaints")

american_forecast <- forecast(american_model, h = 5)
plot(american_forecast, main = "5-Month Forecast for American Eagle", xlab = "Year", ylab = "Complaints")

hawaiian_forecast <- forecast(hawaiian_model, h = 5)
plot(hawaiian_forecast, main = "5-Month Forecast for Hawaiian Airlines", xlab = "Year", ylab = "Complaints")

print("United Airlines Forecast:")
print(united_forecast)

print("American Eagle Forecast:")
print(american_forecast)

print("Hawaiian Airlines Forecast:")
print(hawaiian_forecast)

```

**United Airlines**

- For January 2011, complaints are expected to be around 7,048

- The forecast is less reliable and shows high uncertainty.

**American Eagle**

- For the next 5 months, the predicted complaints are more stable, ranging from 5,335 to 9,013 on average.


**Hawaiian Airlines**

- Complaints for the next 5 months are predicted to remain low and stable, around 2,437 in January 2011.

#### 4. Show the accuracy of your ARIMA model
```{r}
united_accuracy <- accuracy(united_forecast)
print("United Airlines Model Accuracy:")
print(united_accuracy)

american_accuracy <- accuracy(american_forecast)
print("American Eagle Model Accuracy:")
print(american_accuracy)

hawaiian_accuracy <- accuracy(hawaiian_forecast)
print("Hawaiian Airlines Model Accuracy:")
print(hawaiian_accuracy)

```

#### Conclusion

American Eagle has the lowest MAPE, indicating the most accurate model.

United Airlines has moderate MAPE but still better than Hawaiian Airlines.

Hawaiian Airlines higher MAPE could be due to the small scale of complaint values.
